Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-06-26 writeup/pnas-word-order-si.tex
code

	\begin{center}
\begin{tabular}{cccc}
$\lambda=0.0$ & $\lambda=0.9$ & $\lambda=0.9$ & $\lambda=1.0$ \\
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-parseability.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency09.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-efficiency-large.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency10.pdf}
\end{tabular}
	\end{center}
\caption{Results from optimization experiments for different values of $\lambda$, including our two previous preregistered experiments. For comparison, we also show results for $\lambda=0$, corresponding to optimizing for parseability only (same results as reported in Tables (\ref{tab:all-predictions-1}-\ref{tab:all-predictions-2})). For $\lambda=0.9$, we report results from one preliminary preregistered experiment (left) and the final experiment (right). For $\lambda=1.0$, we report the other preliminary preregistered experiment.
Giving similar weight to parseability and predictability -- that is, $\lambda$ close to $1$ -- results in more accurate word order predictions than choosing a small value of $\lambda$ such as $\lambda=0.0$. Note that $\lambda$ cannot take values smaller than zero, or greater than one, see Section \ref{sec:lambda}.
}\label{table:corr-resu-previous}
\end{table}

>>>>

	\begin{center}
\begin{tabular}{cccc}
$\lambda=0.0$ & $\lambda=0.9$ & $\lambda=0.9$ & $\lambda=1.0$ \\
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-parseability.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency09.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-efficiency-large.pdf}&
	\includegraphics[width=0.15\textwidth]{../results/correlations/figures/posterior-satisfied-universals-together-large-prior-efficiency10.pdf}
\end{tabular}
	\end{center}
	\caption{Results from optimization experiments for different values of $\lambda$, including our two previous preregistered experiments (Section~\ref{sec:previous-exps}). For comparison, we also show results for $\lambda=0$, corresponding to optimizing for parseability only (same results as reported in Tables (\ref{tab:all-predictions-1}-\ref{tab:all-predictions-2})). For $\lambda=0.9$, we report results from one preliminary preregistered experiment (left) and the final experiment (right). For $\lambda=1.0$, we report the other preliminary preregistered experiment.
Giving similar weight to parseability and predictability -- that is, $\lambda$ close to $1$ -- results in more accurate word order predictions than choosing a small value of $\lambda$ such as $\lambda=0.0$. Note that $\lambda$ cannot take values smaller than zero, or greater than one, see Section \ref{sec:lambda}.
}\label{table:corr-resu-previous}
\end{table}
